The Concurrent Calculi Formalisation Benchmark

### 2024-02-17 short-paper/short-paper.tex
more coind

\paragraph{Coinduction.} \todo{explain more what the challenge does.}
Coinduction is fundamental to establish properties of processes that
may never terminate, which is a typical situation.
Common uses for coinduction are to define strong and weak versions of
bisimulation, barbed notions of bisimulation, prove trace equivalence,
etc.

We base our challenge around
bisimulation: a fundamental coinductively established property for equating the
observed behaviour of potentially infinite processes. 
In this challenge, we study the notion of strong barbed bisimulation
(and bisimilarity)
over a fragment of the $\pi$-calculus and,
in particular, we focus on obtaining,
from strong barbed bisimilarity,
a congruence with respect to
parallel composition and substitution.

The introduction of bisimulation
is one of the first steps, when studying the
semantics of process calculi, both
in classical textbooks (e.g., \cite{})
and in almost all existent 
mechanisations \cite{}
(where we see a variety
of different choices).

\cite{Castro-Perez2021} note that the most challenging part of their mechanisation was the convoluted definition of infinite behaviours.

>>>>

\paragraph{Coinduction.} \todo{explain more what the challenge does.}
Coinduction is fundamental to establish properties of processes that
may never terminate, which is a typical situation.
Common uses for coinduction are to define strong and weak versions of
bisimulation, barbed notions of bisimulation, and prove trace equivalence. %,
%etc.
On the other hand, coinduction in proof assistants
is notoriously difficult: \lore{add here}
\cite{Castro-Perez2021} note that the most challenging
part of their mechanisation of multiparty session types
was the convoluted definition of infinite behaviours.

We base our challenge around bisimulation: a fundamental coinductively
established property for equating the
observed behaviour of potentially infinite processes. 
In this challenge, we study the notion of strong barbed bisimulation
(and bisimilarity, as in \cite{picalcbook})
over a fragment of the $\pi$-calculus and,
in particular, we focus on obtaining,
from strong barbed bisimilarity,
a congruence with respect to
parallel composition and substitution.

The introduction of bisimulation
is one of the first steps, when studying the
(observable) behaviour of process calculi, both
in classical textbooks (e.g., \cite{picalcbook})
and in almost all existent 
mechanisations, where we see a variety of
different formalisation choices.
As a significative example, we observe that,
while many authors rely
on the native support for coinduction offered by
proof assistants \cite{},
many others prefer a more set-theoretic
approach \cite{}.
